Test susieI using whole genome, s40.22 samples

### 2020-10-24 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
qqplot

```{r gene2}
p3 <- pow(total, n, 0.045, 1e-5)
print(p3)
```

@@

@@

* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize prior for genes and SNPs using true values. gene.pve ~ 0.1, snp.pve ~ 0.5.

>>>>

```{r gene2}
p3 <- pow(total, n, 0.045, 1e-5)
print(p3)
# save(p1,p2,p3, file = "data/power_s40.22.Rd")
```

@@

* Susie run parameters: `L=2`.  We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

@@

* Susie run parameters: `L=2`. We initialize with prior for genes and SNPs using their true values. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).
